### 2024-08-03 conteudo/introduction/intro.tex
add the eval chap on
remove bullshit

Given the unsuccessful results of our search in the formal literature, we started to search for solutions in the 
gray literature, but we ended up without success. In the gray literature, the best solutions we found were 
primitive solutions that find every pair of code files that are duplications. 
The AMD Display driver was created in 20XX (TODO HERE) and maintained until today. The code files that 
contain duplicated code normally also have specific code that is only implemented in this file. 
Thus, a solution that finds duplication in a deeper context is necessary to find correct duplications 
in the Linux kernel context.

@@

This manuscript consists of four more chapters.
Chapter \ref{cha:back} presents the literature overview for code duplication detection (main definitions, 
current approaches in the literature), a brief description of the Linux kernel, and a review of refactoring methods 
used throughout this research.
Chapter \ref{cha:tool} presents our proposed tool to detect code duplication in the Linux kernel, describing all 
the main components.
Chapter \ref{cha:method} describes the research methods selected to guide our work.
Chapter \ref{cha:results} presents the current research stage and the work plan, with the addition of 
preliminary results obtained.

>>>>

Given the unsuccessful results of our search in the formal literature, we started to search for solutions in the 
gray literature, but we ended up without success. In the gray literature, the best solutions we found were 
primitive solutions that find every pair of code files that are duplications. 
The code files on the AMD Display driver that 
contain duplicated code normally also have specific code that is only implemented in this file. 
Thus, a solution that finds duplication in a deeper context is necessary to find correct duplications 
in the Linux kernel context.

@@

This manuscript consists of five more chapters.
Chapter \ref{cha:back} presents the literature overview for code duplication detection (main definitions, 
current approaches in the literature), a brief description of the Linux kernel, and a review of refactoring methods 
used throughout this research.
Chapter \ref{cha:tool} presents our proposed tool to detect code duplication in the Linux kernel, describing all 
the main components.
Chapter \ref{cha:method} describes the research methods selected to guide our work.
Chapter \ref{cha:eval} shows the results obtained of the research methods to evaluate our proposed tool.
Chapter \ref{cha:results} presents the current research stage and the work plan, with the addition of 
preliminary results obtained.
